Self-similarity of the elements of the feasible set

### 2020-08-12 analysis/reports/self_similarity.Rmd
fix na'

nrow(
  comparisons %>%
    select(sim1, sim2) %>%
    distinct()
)

@@

>>>>

@@

```{r comparison 2}

example_fs2 <- readd(fs_s_44_n_13360, cache = cache)

example_di2 <- readd(di_fs_s_44_n_13360, cache =cache)

example_fs2 <- example_fs2 %>%
  left_join(example_di2) %>%
  left_join(net_summary)

comparisons2 <- rep_diff_sampler(example_fs2, ndraws = 100)

both_comparisons <- bind_rows(comparisons, comparisons2) %>%
  mutate(s_and_n = paste0("s_", s0, "_n_", n0))

ggplot(both_comparisons, aes(r2, color = s_and_n)) +
  geom_density() +
  theme_bw() +
  theme(legend.position = "top")

ggplot(both_comparisons, aes(r2_log, color = s_and_n)) +
  geom_density() +
  theme_bw() +
  theme(legend.position = "top")

ggplot(both_comparisons, aes(cd, color = s_and_n)) +
  geom_density() +
  theme_bw() +
  theme(legend.position = "top")

ggplot(both_comparisons, aes(prop_off, color = s_and_n)) +
  geom_density() +
  theme_bw() +
  theme(legend.position = "top")

ggplot(both_comparisons, aes(div, color = s_and_n)) +
  geom_density() +
  theme_bw() +
  theme(legend.position = "top")
